### 2023-08-30 README.Rmd
fin 230829 v_02
230830 new stuff

<li><code>turf</code>: **T**(otal) **U**(nduplicated) **R**(each) and **F**(requency) is a "product line extension model" (Miaoulis et al., 1990, p. 29) that helps to find the perfect product bundle based on the <code>reach</code> (e.g., how many participants consider buying at least one product of that assortment) and the <code>frequency</code> (how many products are on average a purchase option). <code>turf</code> currently provides both the threshold approach (<code>approach = 'thres'</code>; all products that exceed a threshold are considered, e.g., a purchase option; Chrzan & Orme, 2019, p. 112) and the first choice approach (<code>approach = 'fc'</code>; only product with highest utility is considered as purchase option; Chrzan & Orme, 2019, p. 111).

<li><code>freqassort</code>: Similar to <code>turf</code>, <code>freqassort</code>
will give you the averaged frequency, how many products the participants
will choose from your in the function determined potential assortment. 
Again, you have to define a `none` alternative, because `freqassort` uses the *threshold* approach,
meaning if the utility of one product is above the utility of `none`,
it is marked as potential purchase option. While `turf` calculates the reach and frequency for **all** combinations, you specify the combination you are interested in <code>freqassort</code>.</li>

<li><code>reach</code>: Similar to <code>turf</code>,, <code>reach</code> will
give you the averaged percentage of how many participants you can reach
(at least one of the products resemble a purchase option) with your in the function determined
potential assortment. `reach` also uses the *threshold* approach (see above). While `turf` calculates the reach and frequency for **all** combinations, you specify the combination you are interested in <code>reach</code></li>

>>>>

<li><code>turf</code>: <b>T</b>(otal) <b>U</b>(nduplicated) <b>R</b>(each) and <b>F</b>(requency) is a "product line extension model" (Miaoulis et al., 1990, p. 29) that helps to find the perfect product bundle based on the <code>reach</code> (e.g., how many participants consider buying at least one product of that assortment) and the <code>frequency</code> (how many products are on average a purchase option). <code>turf</code> currently provides both the threshold approach (<code>approach = 'thres'</code>; all products that exceed a threshold are considered, e.g., a purchase option; Chrzan & Orme, 2019, p. 112) and the first choice approach (<code>approach = 'fc'</code>; only product with highest utility is considered as purchase option; Chrzan & Orme, 2019, p. 111).</li>

<li><code>freqassort</code>: Similar to <code>turf</code>, <code>freqassort</code>
will give you the averaged frequency, how many products the participants
will choose from your in the function determined potential assortment. 
Again, you have to define a <code>none</code> alternative, because <code>freqassort</code> uses the <i>threshold</i> approach,
meaning if the utility of one product is above the utility of <code>none</code>,
it is marked as potential purchase option. While <code>turf</code> calculates the reach and frequency for <b>all</b> combinations, you specify the combination you are interested in <code>freqassort</code>.</li>

<li><code>reach</code>: Similar to <code>turf</code>, <code>reach</code> will
give you the averaged percentage of how many participants you can reach
(at least one of the products resemble a purchase option) with your in the function determined
potential assortment. <code>reach</code> also uses the <i>threshold</i> approach (see above). While <code>turf</code> calculates the reach and frequency for <b>all</b> combinations, you specify the combination you are interested in <code>reach</code></li>
